---
title: "L_Regression_9.3"
author: "Adriana RM"
date: "9/3/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)
library(gtsummary)
library(dplyr)
library(lme4)


```

## 
```{r}

# Change reference level for RACEi to Non-Hispanc White
dft1 = dft1 %>% mutate(RACEgroup = relevel(RACEgroup,"NHWhite"))

```

## Logistic Regression Ungrouped RACEi

```{r}
## Group RACEi according to:
# For categorizations, we combined race/ethnicity by the following hierarchy:
# ·         Hispanic (any Race)
# ·         Black
# ·         Asian/Pacific Islander 
# ·         non-Hispanic white (NHW)
# ·         Other (Includes American Indian and Alaskan Native)
# ·         Unable to determine

## Create New Race Ethnicity Variable: RACEgroup 
library(forcats)

dft1$RACEgroup <- fct_collapse(dft1$RACEi,
  UTD = "UTD",
  Other = "Native American",
  NHWhite = "Non-Hispanic White",
  Asian_PI = c("Asian", "Pacific Islander"),
  Black = "Non-Hispanic Black",
  Hispanic = "Hispanic"
)

```

## Filter out hospitals with <10

```{r}

#Hospitals with <10 Patients 
dft1 %>% 
  select(COVCLINTRIAL, AGEi, SEX, RACEgroup,psource_group, SRC_FAC_ID) %>%         
  group_by(SRC_FAC_ID) %>% 
  summarise(n_hosp = n()) %>% 
  arrange(desc(n_hosp)) %>% 
  dplyr::filter(n_hosp <10)


#Hospitals with <10 Patients

#DS with summary
dft1 %>% group_by(SRC_FAC_ID) %>% summarise(n_patient = n()) %>%
  arrange(desc(n_patient)) %>% dplyr::filter(n_patient > 10)

#DS with all vars (Keepers)

keep_hosp <-dft1 %>% group_by(SRC_FAC_ID) %>% summarise(n_patient = n()) %>%
  arrange(desc(n_patient)) %>% dplyr::filter(n_patient > 10)


#Filtering out 17 Hospitals that had 10 or less patients 

dim(dft1)
length(unique(dft1$SRC_FAC_ID))

#Use this DF for regression 
filthosp <- dft1[dft1$SRC_FAC_ID %in% keep_hosp$SRC_FAC_ID, , drop = FALSE]

dim(filthosp)
length(unique(filthosp$SRC_FAC_ID))

table(filthosp$COVCLINTRIAL)

```

#Data Processing and Reference Levels: 

```{r}
library(flextable)
library(officer)
library(forcats)

## Check # of NA's: 
#table(filthosp$PATMANICU, useNA = "ifany")

filthosp$PATMANICU <- factor(filthosp$PATMANICU, levels = c("1", "2"),
                            labels=c( "Yes", "No"))
filthosp = filthosp %>%
           mutate(PATMANICU = relevel(PATMANICU, "No"))# 2-not managed in ICU
 
filthosp$PATMANICU <- fct_explicit_na(filthosp$PATMANICU)
filthosp$PATMANICU <- fct_explicit_na(filthosp$PATMANICU, "Miss")

#Reference Levels for Acuity and Death and Race

filthosp = filthosp %>% 
           mutate(death = relevel(death, "0"))# 0-No death

filthosp = filthosp %>% mutate(RACEgroup = relevel(RACEgroup,"NHWhite"))

filthosp = filthosp %>% mutate(COVCLINTRIAL = relevel(COVCLINTRIAL, "Yes"))

#Ensuring Hospital ID and age_group is a factor
filthosp$SRC_FAC_ID <- as.factor(filthosp$SRC_FAC_ID)
filthosp$age_group <- as.factor(filthosp$age_group)

#Set >64 in age_group as reference level 
filthosp = filthosp %>% mutate(age_group = relevel(age_group, ">64"))

table(filthosp$COVCLINTRIAL)
contrasts(filthosp$COVCLINTRIAL)

```

#Regression Model (no psource)

```{r}

fit <- glmer(COVCLINTRIAL ~ SEX + RACEgroup + AGEi + death + PATMANICU + (1|SRC_FAC_ID ),
             data = filthosp,
             family = binomial,
             nAGQ = 1, 
             control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#Model Summary
summary(fit)

#oddsratios.glmm <- exp(1)^fixef(fit)
#print(oddsratios.glmm)

contrasts(filthosp$PATMANICU)
contrasts(filthosp$COVCLINTRIAL)
contrasts(filthosp$SEX)
contrasts(filthosp$RACEgroup)
contrasts(filthosp$age_group)

#Save raw output in txt
sink("mixed_model_raw.txt")
print(summary(fit))
sink()

#Put Summary into Table 

library(gtsummary)

fmodel_tab <- fit %>%
  tbl_regression(exponentiate = TRUE ) %>%
  bold_labels() %>%
  bold_p(t= 0.05)

#Model Table 

fmodel_tab

#Export table into Word

fmodel_flextab <- as_flex_table(fmodel_tab,
                                  include = everything(),
                                  return_calls = FALSE,
                                  strip_md_bold = TRUE)

#Save as a Doc file
docx_file <- tempfile(fileext = ".docx")

save_as_docx("Model" = fmodel_flextab,
              path = docx_file)

View(docx_file)


```

#Regression Model + Payment Source
```{r}

fit2 <- glmer(COVCLINTRIAL ~ SEX + RACEgroup + age_group + death + PATMANICU + psource_group + (1|SRC_FAC_ID ),
             data = filthosp,
             family = binomial,
             nAGQ = 1, 
             control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(fit2)

#Save raw output in txt
sink("mixed_model_raw.txt")
print(summary(fit2))
sink()

#Put Summary into Table 

library(gtsummary)

f2model_tab <- fit2 %>%
  tbl_regression(exponentiate = TRUE ) %>%
  bold_labels() %>%
  bold_p(t= 0.05)

#Model Table 

f2model_tab

#Export table into Word

f2model_flextab <- as_flex_table(f2model_tab,
                                  include = everything(),
                                  return_calls = FALSE,
                                  strip_md_bold = TRUE)

#Save as a Doc file
docx_file <- tempfile(fileext = ".docx")

save_as_docx("Model2" = f2model_flextab,
              path = docx_file)

View(docx_file)

```


## Minimally Adjusted Model 
```{r}
# Estimate the model and store results in m
minadj_fit <- glmer(COVCLINTRIAL ~ SEX + AGEi + (1 | SRC_FAC_ID ),
                         data = filthosp,
                         family = binomial,
                         nAGQ = 1,
                         control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))


# Model Summary: 
summary(minadj_fit)

#Using Sink to get the Raw Outputs
sink("minadj_model_raw.txt")
print(summary(fit))
sink()

#Put Summary into Table 
library(gtsummary)

minadj_tab <- minadj_fit %>%
  tbl_regression(exponentiate = TRUE ) %>%
  bold_labels() %>%
  bold_p(t= 0.05)

minadj_tab

#Export table into Word
minadj_flextab <- as_flex_table(minadj_tab,
                                  include = everything(),
                                  return_calls = FALSE,
                                  strip_md_bold = TRUE)

#Save as a Doc file
docx_file <- tempfile(fileext = ".docx")

save_as_docx("Minimally-adjusted Model" = minadj_flextab,
              path = docx_file)

View(docx_file)

```

#Conditional vs Marginal Coefficients
```{r}
# 
# fm<-mixed_model(fixed = COVCLINTRIAL ~ SEX + RACEgroup + AGEi + death + PATMANICU, random = ~ 1 | SRC_FAC_ID,
#              data = filthosp,
#              family = binomial())
# summary(fm)
# 
# #Getting Conditional Odds Ratio
# conditionalOR<-exp(confint(fm, level = 0.95))
# 
# conditionalOR
# 
# sink("conditional_OR_mixed_model.txt")
# print(conditionalOR)
# sink()
# 
# marginals<-marginal_coefs(fm, std_errors = TRUE, cores = 3)
# 
# marginals
# 
# MarginalOR95<- exp(confint(marginals, level = 0.95))
# 
# MarginalOR95
# 
# #Using Sink to get the Raw Outputs
# sink("marginal_OR95.txt")
# print(MarginalOR95)
# sink()
# 
# 
# MarginalOR<-exp(coef(marginals))
# 
# #Using Sink to get the Raw Outputs
# sink("marginal_OR.txt")
# print(MarginalOR)
# sink()
# 
# 
# #Using Sink to get the Raw Outputs
# sink("marginal_coefficients_mixed_model.txt")
# print(marginals)
# sink()
# 
# ```
# 
# ```{r}
# ## Unadjusted Odds Ratios 
# 
# ##Question: Keep clustering by hospital?
# 
# #RACEgroup
# 
# unadj<-mixed_model(fixed = COVCLINTRIAL ~ RACEgroup,
#             random = ~ 1 | SRC_FAC_ID,
#             data = filthosp,
#             family = binomial())
# 
# summary(unadj)
# 
# #Getting Conditional Odds Ratio
# conditionalOR<-exp(confint(unadj, level = 0.95))
# 
# conditionalOR
# 
# conOR<-round(conditionalOR,2)
# 
# sink("conditional_OR_unadj_RACEgroup.txt")
# print(conOR)
# sink()
# 
# marginals<-marginal_coefs(fm, std_errors = TRUE, cores = 3)
# 
# marginals
# 
# MarginalOR95<- exp(confint(marginals, level = 0.95))
# 
# MarginalOR95

```


