---
title: "Visualizations"
author: "Adriana RM"
date: "8/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r cars}
#Visualizing the Data
```{r Visualizations, echo=FALSE}
#Age for the entire sample
ggplot(dft1) +
 aes(x = AGEi) +
 geom_histogram(bins = 100L, fill = "#6dcd59") +
 labs(x = "Age", y = "Count") +
 theme_classic()
```
#Visualizing the Data
```{r Vis (age/sex) in Enrolled vs Not Enrolled, echo=FALSE}
#Age and Sex comparison Enrolled vs Not-Enrolled

dft1 %>%
 filter(!is.na(SEX)) %>%
 filter(!is.na(AGEi)) %>%
 filter(!is.na(COVCLINTRIAL)) %>%
 ggplot() +
 aes(x = AGEi, fill = SEX) +
 geom_histogram(bins = 18L, position = "dodge") +
 scale_fill_hue() +
 labs(x = "Age", y = "Count", title = "Enrolled/Not Enrolled", fill = "Sex") +
 theme_classic() +
 facet_wrap(vars(COVCLINTRIAL), scales = "free_y")

```
#Visualizing the Data

```{r Race Comparison - Enrolled vs Not Enrolled, echo=FALSE}

library(dplyr)
library(ggplot2)

melted<-melt(dft1$RACEi, dft1$COVCLINTRIAL, id=PATIENT_ID )

#Manipulating DAta With Denominator  

dat <-dft1 %>%
  select(RACEi, COVCLINTRIAL) %>%
  tidyr::gather(RACEi, COVCLINTRIAL, na.rm = FALSE, convert = FALSE, factor_key = FALSE) %>%
  count(RACEi, COVCLINTRIAL) %>%
  group_by(COVCLINTRIAL) %>%
  mutate(percent = (n/sum(n) * 100)) %>%
           mutate (rounded = round(percent, 1))

dat

#With Denominator

dft1 %>%
  group_by(RACEi, COVCLINTRIAL) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  mutate(percent = (freq*100))

byrace<-dft1 %>%
  group_by(RACEi, COVCLINTRIAL) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  mutate(percent = (freq*100), rounded = round(percent,1))


sink("output.txt")
byrace
sink()
```

```{r}
#PLOT
ggplot(dat, aes(RACEi, percent, fill = COVCLINTRIAL)) + 
    geom_col(position = "stack") + 
  labs(x = "Race", y = "Percentage",
       title = "Percentage of Patients Enrolled/Not Enrolled in Clinical Trials by Race",
       fill = "Enrolled") + scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 25)) +
   geom_label(aes( label = "rounded",
                y= "rounded",
           position = "stack",
           vjust = 0.5))+
  theme_classic() +
  coord_flip()

 aes(x = reorder(Name, -Number), Number)

#Plot 2
 png("myplot.png")
 
p1 <- ggplot(data = dat, aes(y= percent, x= reorder(RACEi, -rounded), fill=COVCLINTRIAL)) + 
  geom_bar(stat="identity", width = 0.8) + 
  ggtitle("Figure 1. Percentage of Enrollment in Clinical Trials") +
  xlab('Race/Ethnicity') + ylab('Percentage') +
  # geom_text(aes(x = RACEi, label = paste0(rounded, '%')), 
  #           colour = 'white',
  #           size= 3,
  #           position=position_stack(vjust=0.5)) + 
  labs(fill='Enrolled') +
  theme_classic() + 
  coord_flip()

p1

file1 <- tempfile("file1", fileext = ".png")
save_plot(file1, p1)
View(file1)

# PLot Percentage of Enrollment by Race/Ethnicity

p2 <- ggplot(data = byrace, aes(y= percent, x= reorder(RACEi, -percent), fill=COVCLINTRIAL)) + 
  geom_bar(stat="identity", width = 0.8) + 
  ggtitle("Figure 1. Percentage of Enrollment in Clinical Trials") +
  xlab('Race/Ethnicity') + ylab('Percentage') +
   geom_text(aes(x = RACEi, label = paste0(rounded, '%')), 
             colour = 'white',
             size= 2.7,
             position=position_stack(vjust=0.5)) +
  labs(fill='Enrolled') +
  theme_classic() + 
  coord_flip()

p2

file1 <- tempfile("file1", fileext = ".png")
save_plot(file1, p2)
View(file1)

```

```{r}
#PLot 2 with Labels 

ggplot(dft1, aes(x= RACEi, group= COVCLINTRIAL)) + 
    geom_bar(aes(y = ..prop.., fill = factor(COVCLINTRIAL)),
             stat="count",
             position = "stack") +
 geom_text(aes( label = scales::percent(..prop..),
                y= ..prop.. ),
              stat= "count",
           position = "stack",
           vjust = 0.5) +
      labs(y = "Percent",
         fill= "COVCLINTRIAL",
         position = "stack",
         vjust = .5) +
       scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) + 
        theme_classic() + 
        coord_flip()
```


```{r}

library(esquisse)
library(ggplot2)

ggplot(dft1) +
 aes(x = RACEgroup, fill = RACEgroup) +
 geom_bar(aes(y = (..count..)/sum(..count..)), position = "dodge") +
 scale_fill_hue() +
 labs(x = "Race", y = "%", title = "Enrolled vs Not Enrolled in Clinical Trials by Race") +
 theme_classic() + scale_y_continuous(labels = scales::percent_format(accuracy=1.000)) +
 scale_y_continuous(limits = c(0, 0.4), breaks = seq(0, 0.4, by = 0.05), labels = scales::percent_format(accuracy=1.00)) +
 theme(legend.position = "none") +
 facet_wrap(vars(COVCLINTRIAL))

# ggplot(dft1) +
#  aes(x = COVCLINTRIAL, fill = RACEgroup, group = RACEgroup) +
#   geom_bar(aes(y = (..count..)/sum(..count..)), position = "dodge") +
#  scale_fill_hue() +
#  labs(x = "Enrolled", y = "%", title = "Enrolled vs Not Enrolled in Clinical Trials by Race") +
#  theme_classic() +
#  scale_y_continuous(limits = c(0, 0.4), breaks = seq(0,0.4, by = 0.05), labels = scales::percent_format(accuracy=1.00)) +
#  theme(legend.position = "none") +
#  facet_wrap(vars(RACEgroup))

```

```{r}
library(ggplot2)

ggplot(dft1) +
 aes(x = RACEgroup, fill = RACEgroup) +
 geom_bar(position = "dodge") +
 scale_fill_hue() +
 labs(x = "Race", y = "Count", title = "Enrolled vs Not Enrolled in Clinical Trials", fill = "Race") +
 theme_classic() +
 facet_wrap(vars(COVCLINTRIAL))

ggplot(dft1) +
 aes(x = COVCLINTRIAL, fill = RACEgroup) +
 geom_bar(position = "dodge") +
 scale_fill_hue() +
 labs(x = "Enrolled/Not-Enrolled", y = "Count", title = "Enrolled vs Not Enrolled in Clinical Trials by Race", fill = "Race") +
 theme_minimal() +
 theme(legend.position = "none") +
 facet_wrap(vars(RACEgroup))

ggplot(dft1) +
 aes(x = COVCLINTRIAL, fill = RACEgroup) +
 geom_bar(position = "dodge") +
 scale_fill_hue() +
 labs(x = "Enrolled/Not-Enrolled", y = "Count", title = "Enrolled vs Not Enrolled in Clinical Trials by Race", fill = "Race") +
 theme_classic() +
 theme(legend.position = "none") +
 facet_wrap(vars(RACEgroup))

dft1 %>%
 filter(!(RACEgroup %in% c("Other", "UTD"))) %>%
 ggplot() +
 aes(x = COVCLINTRIAL, fill = RACEgroup) +
 geom_bar(position = "dodge") +
 scale_fill_hue() +
 labs(x = "Enrolled/Not-Enrolled", y = "Count", title = "Enrolled vs Not Enrolled in Clinical Trials by Race", fill = "Race") +
 ggthemes::theme_fivethirtyeight() +
 theme(legend.position = "none") +
 facet_wrap(vars(RACEgroup))

dft1 %>%
 filter(!(RACEgroup %in% c("Other", "UTD"))) %>%
 ggplot() +
 aes(x = COVCLINTRIAL, fill = RACEgroup, group = RACEgroup) +
 geom_bar(position = "dodge") +
 scale_fill_hue() +
 labs(x = "Enrolled/Not-Enrolled", y = "Count", title = "Enrolled vs Not Enrolled in Clinical Trials by Race", fill = " ") +
 ggthemes::theme_fivethirtyeight()
```

```{r}

```


