---
title: "Visualizations"
author: "Adriana RM"
date: "8/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r cars}
#Visualizing the Data
```{r Visualizations, echo=FALSE}
#Age for the entire sample
ggplot(dft1) +
 aes(x = AGEi) +
 geom_histogram(bins = 100L, fill = "#6dcd59") +
 labs(x = "Age", y = "Count") +
 theme_classic()
```
#Visualizing the Data
```{r Vis (age/sex) in Enrolled vs Not Enrolled, echo=FALSE}
#Age and Sex comparison Enrolled vs Not-Enrolled

dft1 %>%
 filter(!is.na(SEX)) %>%
 filter(!is.na(AGEi)) %>%
 filter(!is.na(COVCLINTRIAL)) %>%
 ggplot() +
 aes(x = AGEi, fill = SEX) +
 geom_histogram(bins = 18L, position = "dodge") +
 scale_fill_hue() +
 labs(x = "Age", y = "Count", title = "Enrolled/Not Enrolled", fill = "Sex") +
 theme_classic() +
 facet_wrap(vars(COVCLINTRIAL), scales = "free_y")

```
#Visualizing the Data
```{r Race Comparison - Enrolled vs Not Enrolled, echo=FALSE}
library(dplyr)
library(ggplot2)

#Working on this... 
ggrc<- dft1 %>%
 ggplot() +
 aes(x = RACEi, fill = RACEi) +
 geom_bar(aes(y = (..count..)/sum(..count..))) +
 scale_fill_hue() + scale_y_continuous(labels = scales::percent) +
 labs(title = "Enrolled Vs Not-Enrolled in Clinical Trials by Race") +
 theme_classic() +
 coord_flip() +
 facet_wrap(vars(COVCLINTRIAL), scales = "free")





```
